---
title: "Ramen Ratings"
author: "Yvonne Lam"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(stringr)
library(shiny)
library(shinyWidgets)
library(leaflet)
library(plotly)
library(DT)
library(rsconnect)

#read data
ratings <- read.csv("ramen-ratings.csv")
str(ratings)

#clean data
unique(ratings$Stars)
ramen_ratings <- ratings %>% 
  filter(Stars != "Unrated", Style != "")

ramen_ratings$Style <- droplevels(ramen_ratings$Style)

ramen_ratings$Stars <- as.numeric(as.character(ramen_ratings$Stars))
ramen_ratings$Variety <- as.character(ramen_ratings$Variety)
ramen_ratings$Top.Ten <- as.character(ramen_ratings$Top.Ten)
ramen_ratings$Country <- as.character(ramen_ratings$Country)

head(ramen_ratings)

```


```{r}
#fix the country entries on ramen_ratings df
ramen_ratings$Country <- str_replace(ramen_ratings$Country, "Dubai", "United Arab Emirates")
ramen_ratings$Country <- str_replace(ramen_ratings$Country, "Holland", "Netherlands")
ramen_ratings$Country <- str_replace(ramen_ratings$Country, "Sarawak", "Malaysia")
ramen_ratings$Country <- str_replace(ramen_ratings$Country, "UK", "United Kingdom")
ramen_ratings$Country <- str_replace(ramen_ratings$Country, "USA", "United States")


```



Sidebar {.sidebar data-width=300}
=============

### Dropdown Menu
```{r}
pickerInput(inputId = "dropdown_countries",label = "Select countries:", 
            choices = sort(unique(ramen_ratings$Country)), 
            multiple = TRUE, options = list('actions-box' = TRUE))

#global filtered dataframe
filtered_df <- reactive({
  ramen_ratings %>% 
  filter(Stars >= input$slider_ratings[1], Stars <= input$slider_ratings[2],
         Style %in% input$checkbox_packagingstyle,
         Country %in% input$dropdown_countries)
})
```


### Checkbox
```{r}
checkboxGroupInput(inputId = "checkbox_packagingstyle", label = "Choose packaging style:", choices = sort(unique(ramen_ratings$Style)), select = "Pack")
```

### Ratings Slider

```{r}
sliderInput(inputId = "slider_ratings",label = "Select rating range:",min = 0.0, max = 5.0, value = c(3.0,4.0), step = 0.125)
```

Plots
===

Column {.tabset data-width=700}
--------------

### How to Use

This dashboard is based on the open data available from the Ramen Rater website (https://www.theramenrater.com/resources-2/the-list/). The data is a compilation of instant noodles reviews all from one person.  
  
The global sidebar can be used to filter the data(instant noodles reviews) according to user inputs (countries selected, ramen packaging style and its ratings). In this context, **countries** refer to the main consumer markets which the brands target. The **ratings** refer to the number of Stars, out of a possible 5, which the reviewer has given to that particular instant noodle product.  

This dashboard has 2 Column Charts, 1 World Map and 1 Data Table.  
**Column charts**  
1. Ratings per Country: shows how well the average product fares against other countries' instant noodles  
2. Brands per Country: indicates the relative demand & supply of instant noodles in that market  
**World Map**: shows the brands found in a country on a visual world map  
**Data Table**: full details of the selected data are listed out

### Ratings per Country
```{r}

#average rating by country of filtered df
ratings_vs_country <- reactive({
  filtered_df() %>%  
  group_by(Country) %>%
  summarise(avg_rating = mean(Stars)) %>% 
  ungroup()
})

#global average rating-fixed value
avg_rating_overall <- ramen_ratings %>% 
  group_by(Country) %>%
  summarise(avg_rating = mean(Stars)) %>% 
  ungroup()
avg_rating_overall <- mean(avg_rating_overall$avg_rating)

#plot ratings vs country
countryplot <- reactive({
  ratings_vs_country() %>% 
  mutate(diff = avg_rating - avg_rating_overall) %>% 
  mutate(highlow = ifelse(diff > 0, "high", "low"))
})

renderPlotly(
plot_ly(countryplot(),
          y= ~reorder(Country,avg_rating),
          x= ~avg_rating, 
          type= ~"bar", color=~highlow,
          orientation= "h",
          showlegend= FALSE) %>% 
  add_trace(x=avg_rating_overall, type= "scatter", mode= "lines+markers", 
            showlegend=FALSE, marker=list(color="orange")) %>% 
  layout(title="Ratings vs Country",
         xaxis= list(title="Average Rating (Stars)"),
         yaxis= list(title="Country", dtick =1))
)

```

### Brands per Country
```{r}
#no. of brands vs country

#group brands by country from filtered df
brands_vs_country <- reactive({
  filtered_df() %>% 
  group_by(Country) %>%
  summarise(count = n_distinct(Brand), brand_list = Brand %>% unique %>% sort %>% paste(collapse = ", ")) %>% 
  ungroup()
})

renderPlotly(
ggplot(brands_vs_country(), aes(x= reorder(Country,count),y= count))+
  geom_col()+
  labs(title="No. of Brands per Country", x="Target Market (Country)", y="No. of Brands")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust= 1))
)
```


Column {data-width=300}
---------------

### Total Reviews (ValueBox)
```{r}
renderValueBox(
valueBox(value = filtered_df() %>% count(),
         caption= "Total Reviews",
         icon= "fa-pen",
         color = "skyblue")
)
```

### valuebox2
```{r}
valueBox(value = signif(avg_rating_overall, 3),
         caption= "Global Average Rating",
         icon= "fa-star",
         color = "orange")
```


World Map
===

### Map

```{r}
countries_coords <- read.csv("countries-geog-coordinates.csv", stringsAsFactors = FALSE)
countries_coords$name[[143]] <- "Myanmar"

#filter out redundant country coordinates
ramen_countries <- countries_coords %>% 
  filter(name %in% ramen_ratings$Country) %>% 
  select(c(4,3,2))

#check no. of countries are correct after filtering (all_ctry is complete list, ramen_countries is not)
all_ctry <- sort(unique(ramen_ratings$Country))

#combine coords df with brands_vs_country df
countries_brands <- reactive({
  merge(ramen_countries, brands_vs_country(), by.x="name", by.y="Country")
})

renderLeaflet(
leaflet() %>% 
  addProviderTiles("Esri.WorldStreetMap") %>%
  addCircleMarkers(lng = ramen_countries$longitude,
             lat = ramen_countries$latitude,
             label = ramen_countries$name) %>% 
  addMarkers(lng = countries_brands()$longitude,
                   lat = countries_brands()$latitude,
                   popup = paste(countries_brands()$name, "<br>",
                                 "No. of Brands:", countries_brands()$count, "<br>",
                                 "Brands: ", countries_brands()$brand_list))
)
```

Data Table {data-navmenu=More}
===

### Data Table

```{r}

renderDataTable(
datatable(filtered_df() %>% 
             select(c(2,3,4,5,6))
          )
)
```

LBB Task {data-navmenu=More}
===

### Details

Dear Participants,
Congratulations! You have completed "Interactive Plotting" workshop. In addition, please kindly complete the "Learn-By-Building: Interactive Plotting".

You have to create your own interactive dashboard (flexdashboard/shiny/shiny dashboard) and submit it as your final project for this workshop. Here are further details regarding your "Learn-By-Building: Interactive Plotting":

a. Use dataset we covered in class or your own dataset (open data from internet or etc).

b. Create an interactive dashboard (flexdashboard/shiny/shiny dashboard/ interactive document) by applying what you’ve learned in the workshop (dplyr, plotly), you can apply any theme to your web dashboard.

The web dashboard must feature an input panel that accepts end user inputs and render the output accordingly.

If you're using your own case dataset, please upload your data in google drive and also send us the link. (you may also anonymizes if you find your data is sensitive)

After you finished your assignment, please submit your file and link (if you publish your dashboard) here.

